Minimizing post-shock forecasting error using disparate information

### 2020-08-05 manuscript/fig2.tex
addition of Section 3.4 and many revisions to abstract, intro, and Section 3.3, 4, 5, 6
changes by deletion of covariates and revision by comments

% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
	(481.73, 86.67) --
	(476.44, 86.67) --
	(479.09, 91.25);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-05 10:48:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 92.09) --
	(481.73, 87.51) --
	(476.44, 87.51) --
	(479.09, 92.09);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 89.61) -- (481.86, 89.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 86.84) -- (479.09, 92.39);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 83.03) -- (481.05, 86.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.95) -- (481.05, 83.03);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}
